---
title: "Lab1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Create a dataframe capable of representing the design, in as complete a way as you can. (0/100)

```{r}

n <- 36
OL <- 3
IL <- 3

design <- matrix(4, ncol=3, nrow=3)
colnames(design) <- c("OL_2","OL_4","OL_8")
row.names(design) <- c("IL_0","IL_4","IL_8")

subjects <- 1:36
OL <- rep(c(2,4,8), 12)
IL <- rep(c(0,4,8), each=12)
recall <- sample(0:20, 36, replace=TRUE)

long_design <- tibble(subjects,
                      OL,
                      IL,
                      recall)
library(tidyverse)
library(dplyr)
long_design %>%
  group_by(OL,IL)%>%
  count()

# mixed design

mixed_design <- tribble(
  ~Subjects, ~OL, ~IL,
  #--|--|---
  1, 2, 0,
  1, 4, 4,
  1, 8, 8,
  3, 6, 4,
  5, 6, 8,
  9, 4, 2,
  2, 1, 9,
  8, 7, 6,
  8, 2, 0,
  5, 6, 8,
  9, 4, 2,
  2, 1, 9,
  9, 4, 2,
  2, 1, 9,
  8, 7, 6,
  1, 4, 4,
  1, 8, 8,
  3, 6, 4,
  5, 6, 8,
  9, 4, 2,
  2, 1, 9,
  9, 6, 2,
  9, 4, 2,
  2, 1, 9,
  9, 4, 2,
  1, 8, 8,
  3, 6, 4
)

mixed_design %>%
  group_by(OL,IL)%>%
  count()

full_mixed_design <- rbind(mixed_design,
                           mixed_design,
                           mixed_design,
                           mixed_design)%>%
  mutate(Subjects = rep(1:36, each=3),
         recall = sample(0:20,36*3, replace = TRUE))

full_mixed_design %>%
  group_by(OL,IL) %>%
  summarize(mean_recall = mean(recall), .groups="drop")


```

Question: What was the broad question? What was the specific question?
- Broad: How much does practicing something effect recall?  
- Specific: Does the amount of learning practice impact retroactive inhibition?

Alternative hypotheses: What were the hypotheses?
- As amount of practice in interpolated learning decreases, retroactive inhibition will increase
- As original learning practice increases, retroactive learning will decrease.

Logic: If hypothesis 1 was true, what was the predicted outcome? What was the predicted outcome if hypothesis 2 was true?
- The more a participant practices IL, the fewer words they will be able to recall
- The more original learning increases, the more words they will be able to recall

Method: What was the experimental design?
- factorial design
- Participants were presented with four pairs of sentences to learn
	- one pair was practice
	- first passage of each pair was for original learning
	- second passage of each pair was for interpolated learning
- Degrees of OL = 3 (2, 4, 8 trials)
- Degrees of IL = 3 (0, 4, 8 trials)
- procedure
	- warm-up color guessing
	- instructions for serial anticipation
	- assigned number of OL trials
	- assigned number of IL trials (IL 0 was another color guessing activity)

Results: What was the pattern of data?
- Both variables increased recall
- RI decreased as a function of increasing OL and decreasing IL practice

Inferences: What can be concluded about the hypotheses based on the data? What can be concluded about the specific and broad question? What are the next steps?
- The data supports the hypotheses
- Original learning is more effective than interpolated learning when it is connected discourse
- Original, or exploratory learning has better results for recall than repetition based memorization techniques
